Model 

### 2019-10-03 04_estimation.Rmd
Export models estimated without lagged accessibility coefficients

```{r physact_sdem}
access_sdem_wc <- errorsarlm(update(base_formula, physact ~ . + 
                                      log(lag.density) + log(lag.income) + 
                                      lag.fulltime + lag.college + lag.single + lag.youth + 
                                      lag.young_adults + lag.seniors + lag.black + lag.asian + 
                                      lag.hispanic + lag.other + access_ls),
                             data = contiglagged_tracts, listw = Wcontig, zero.policy = TRUE)
```

@@

```{r models}
write_rds(slx_vs_sdem, "data/slx_vs_sdem.rds")
write_rds(pa_models, "data/pa_models.rds")
write_rds(obesity_models, "data/obesity_models.rds")
```

>>>>

```{r nolag_access}
access_slx_wc <- lm(update(
  base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
    lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls),
  data = contiglagged_tracts)

access_sdem_wc <- errorsarlm(update(
  base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
    lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls), 
  data = contiglagged_tracts, listw = Wcontig, zero.policy = TRUE)
```

```{r nolag_access_tests}
slx_hausman(access_slx_wc, access_sdem_wc)
slx1_vs_sdem1 <- list("SLX" = access_slx_wc, "SDEM" = access_sdem_wc)

screenreg(slx1_vs_sdem1, ci.force = TRUE)
```

@@

```{r models}
write_rds(slx1_vs_sdem1, "data/slx_vs_sdem.rds")
write_rds(pa_models, "data/pa_models.rds")
write_rds(obesity_models, "data/obesity_models.rds")
```
